Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-06-11 response.tex

\usepackage{color}
\usepackage{fullpage}

\def\BibTex{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
         T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\usepackage{amsmath}
\usepackage{amssymb}

% Citations et bibliographie style Harvard
\usepackage[agsm,dcucite]{harvard}
\renewcommand{\harvardand}[1]{\& }
\renewcommand{\harvardurl}[1]{\url{#1}}
\newcommand{\citefullname}[2]{#2 \citeasnoun{#1}}

\newcounter{pointno}
\setcounter{pointno}{0}
\def\thepoint{\arabic{pointno}}
\newcommand{\ptno}[1]{\textcolor{blue}{\refstepcounter{pointno} \thepoint. \#1}}
\newcommand{\question}[1]{\bigskip{\it\ptno{\#1}}}
% \def\answer{}

@@

\title{Response to the reviewers on “Sufficient Conditions for Reachability in Automata Networks with Priorities”}
\author{Maxime Folschette, Loïc Paulevé, Morgan Magnin, Olivier Roux}
\date{}

\begin{document}

\maketitle

We wish to thank the reviewers for their comments.
Following reviewers comments,
with this revision
we added
  several paragraphs of informal explanations to give more intuition 
  for technical definitions (in particular in section 3);
  and simplified a few notations.

@@

\section*{Comments and answers to the reviewers}

\subsection*{Reviewer \#1}

1) somehow the system of AANs seems such that it has conection or roots or generalization by cellural automata. Obviously, CA are a more general model and AANs are a restriction, but it could be interesting to see whether can you generalize or simulate in simple manners your system with CA?

\ilanswer{
Contrary to cellular automata, the neighbourhoods in AANs are not regular
(each component has its own regulation rules).
One can thus straightforwardly encode finite cellular automata
with an asynchronous semantics into AANs.
}

@@

\medskip

\noindent
2) Just a note: As I see it, the AANs is an interactive model of computation, and that is interesting. based on this, can you consider the reachability of state as a game in (multiplayer) game of AAN? Does  your work give a fast method for checking for winning strategy?

@@

%     In a nutshell, although it is theoretically feasible, more analyses are required in order to judge if the conclusiveness is satisfying enough.
% \end{itemize}
% }

\ilanswer{
Our analysis focuses on finding sufficient conditions for achieving a
reachability goal, but does not account for an “opposing player” which would
try to prevent the concerned reachability to occur.
Therefore our analysis is not directly applicable in such a game theory setting.
However, it can be used to solve cooperation games
(where all players cooperate in reaching the goal).
}

@@

\answer{
We have added a word about these subjects in the conclusion of the article.
}

\noindent
Minor coments to the authors:

\answer{Except the comment below, we have taken all minor comments into account.}

\noindent
page 1, authors: names are not in alphabetical order probably for a good reason, but it strikes my mathematician eye badly.

\answer{We willingly chose the order of the authors' names related to the individual participation
of each one (following the common practice in computational systems biology community).}

@@

\subsection*{Reviewer \#2}

My main concern about the paper is that it is written in a rather unclear manner. Some of the definitions are given in a very formal way; this does not help understanding the intuition behind them. On the other hand, the authors have managed to give a very good intuition in description of the running examples of the paper.

In my opinion, the presentation of the material of the paper should be improved.

\answer{Our aim was to achieve a double understanding from the reader,
by presenting our definitions and results both in an informal and intuitive manner,
so that readers can easily understand the background idea,
and in a formal way in order to avoid any ambiguities.
Therefore, we prefer not to make the definitions and theorems less formal.
However, we added several paragraphs of explanations around the definition of the Local Causality Graph (Def. 7; previously Def. 8) to ease its understanding.
Furthermore, we have removed the notion of context from the body of the paper,
which allows some notation simplification without weakening the presented results.
}

\noindent
COMMENTS TO AUTHORS

@@

\answer{Except the comment below, we have taken all comments to authors into account.}

\noindent
page 7, Definition 4, line 55, in the sentence "The set of all objectives is called ..." ---
Using the logical AND operator "$\land$" is too formal and this unnecessarily complicates reading of the definition.
I would replace "$\land$" with a word "and".

### 2015-06-11 parts-sa.tex
minor change
minor modifications bis

\modmf{%
The previous subsections permitted to define all the tools needed to build the Local Causality Graph (LCG).
This graph is denoted $\cwB$ where $u$ is the local state to be reached
from the initial state $s$.
It will be the basis of our static analysis,
as it represents the causality links between the different objectives involved
in the solving of the reachability of $u$.
This LCG is built recursively by considering some required local states (\eg $u$),
linking them to objectives (\eg $\PHobj{t}{u}$, if $t \in s$),
and locally refining these objectives in order to include new required local states
from other automata.
An example of LCG is depicted in \pref{fig:sa-livelock}.
}

@@

\modmf{%
Finally, we note that
the LCG of \pref{def:lcg} contains synchronizing nodes ($\sSol$)
that allow to express the need for several local states simultaneously
in order to play a given action.
This is the main difference regarding~\cite{PMR12-MSCS}
which tackled with Process Hitting, whose actions are limited to at most one hitter
and thus did not require this kind of synchronization.
However, \pref{def:lcg} is equivalent to the definition of the structure
given in~\cite{FPMR13-CS2Bio},
although it was adapted for AANs which notably allowed to simplify its formalism.
}

>>>>

\modmf{%
The previous subsections \modLP{introduced the necessary definitions to build the
so-called} Local Causality Graph (LCG).
This graph is denoted $\cwB$ where $u$ is the local state to be reached
from the initial state $s$.
It will be the basis of our static analysis,
as it represents the causality links between the different objectives involved
in the solving of the reachability of $u$.
This LCG is built recursively by considering some required local states (\eg $u$),
linking them to objectives (\eg $\PHobj{t}{u}$, if $t \in s$),
and locally refining these objectives in order to include new required local states
from other automata.
An example of LCG is depicted in \pref{fig:sa-livelock}.
}

@@

\modmf{%
Finally, we note that
the LCG of \pref{def:lcg} contains synchronizing nodes ($\sSol$)
that allow to express the need for several local states simultaneously
in order to play a given action.
This is the main difference regarding~\cite{PMR12-MSCS,FPMR13-CS2Bio}
which tackled with Process Hitting, whose actions are limited to at most one hitter
and thus did not require this kind of synchronization.
}
%However, \pref{def:lcg} is equivalent to the definition of the structure
%given in~\cite{FPMR13-CS2Bio},
%although it was adapted for AANs which notably allowed to simplify its formalism.
